Exploring Potential 6LoWPAN Traffic Side Channels

### 2017-04-06 Writing/iotprotocols.tex
Update  # Changes to be committed:

%Avaible security options.
For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}. 802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network. tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively. We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously as the resulting packets exceeded the 802.15.4 MTU\footnote{Maximum Transmission Unit.} and thus not practical.

>>>>

%Avaible security options.
For our settings, there are two schemes available for packet encryption, namely 802.15.4 Security\cite{802154} and DTLS\cite{rfc6347}. 802.15.4 Security is provided by noncoresec\cite{noncoresec} which implements 802.15.4 authenticated encryption with AES-128 CCM*\cite{CCM} using a hard-coded key shared by the whole 6LoWPAN network. tinyDTLS\cite{tinydtls} provides a minimum DTLS implementation that supports only two ciphersuites which are TLS\_PSK\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} and TLS\_ECDHE\_ECDSA\_WITH\_AES\_128\_CCM\_8\cite{rfc6655} respectively. We do not concern the case where both 802.15.4 Security and DTLS are enabled simultaneously, as the de facto encryption schemes are both AES-128 CCM* and overlapping them does not enhance the security but only increases the overhead.

### 2017-04-06 Writing/submission.tex
First draft [IoT Protocols] uploaded. Included packages.tex and appendix in submission.tex.
Update  # Changes to be committed:

%Literatures about 6LoWPAN security
With regard to the aspect of protocol design, the recent paper \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including its susceptibility to the Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}. In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}.

TODO: if space and time say some more about these attacks. At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess).

@@

%\appendix

%And this is my Appendix.

>>>>

%Literatures about 6LoWPAN security
With regard to the aspect of protocol design, the recent paper \cite{6LoWPANAtk} summarised some known flaws of 6LoWPAN, including its susceptibility to the Fragmentation Attack\cite{FragAtk}, Sinkhole Attack\cite{Sinkhole}, Hello Flood Attack\cite{HelloFlood}, Wormhole Attack\cite{Wormhole} and Blackhole Attack\cite{Blackhole}. In addition, \cite{802154SecIssues} reported certain problematic designs in 802.15.4 security\cite{802154}. However we do not discuss further about these designing flaws as they lay into a different aspect of the security issues addressed by this paper.

%\textbf{TODO: if space and time say some more about these attacks. At least say if they relate to the type of leakage we are exploiting or if they are completely independent (which is what I would guess). }

@@

\appendix
\input{appendix}
%And this is my Appendix.
